Paper_analyses

### 2021-07-22 Paper_Analyses_subj_obje_arousal.Rmd
Timecourse pupil
line 392
- added the timecourse model for pupil.

Todo - solve the warnings and converegence errors and make one plot with all effects. also imclue velocity

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

@@

car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4

@@

@@

@@

>>>>

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

# relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
# max(abs(relgrad))0.0002044252

@@

# car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4

@@

# export model table
library(MuMIn)
library(sjmisc)
sjPlot::tab_model(pupil_arousal_findings$pupil_from_ar_vale)

@@

Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
Formula: pup_basCor ~ (valence_c * arousal_c) + Mean_gray_z + (1 + Mean_gray_z |  
    ssid) + (0 + valence_c * arousal_c | ssid)
   Data: subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier ==      FALSE & ssid_num < 500 & arousal_outler == FALSE)

     AIC      BIC   logLik deviance df.resid 
  8493.9   8579.2  -4231.9   8463.9     2170

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-3.6141 -0.5987  0.0067  0.5952  3.6796

Random effects:
 Groups   Name                Variance Std.Dev. Corr       
 ssid     (Intercept)         0.78415  0.8855              
          Mean_gray_z         0.13611  0.3689   0.55       
 ssid.1   valence_c           0.04233  0.2057              
          arousal_c           0.02296  0.1515    0.89      
          valence_c:arousal_c 0.01700  0.1304   -0.19  0.01
 Residual                     2.57999  1.6062              
Number of obs: 2185, groups:  ssid, 43

Fixed effects:
                    Estimate Std. Error       df t value             Pr(>|t|)    
(Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
valence_c            0.08546    0.06557 28.33677   1.303              0.20294    
arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
Mean_gray_z         -0.96311    0.06622 43.35750 -14.544 < 0.0000000000000002 ***
valence_c:arousal_c  0.15461    0.04434 24.37046   3.487              0.00187 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Correlation of Fixed Effects:
            (Intr) vlnc_c arsl_c Mn_gr_
valence_c   -0.042                     
arousal_c   -0.031  0.746              
Mean_gray_z  0.453 -0.013  0.028       
vlnc_c:rsl_  0.147 -0.267 -0.128  0.035

@@

Timecourse analyses

# prepare timecourse data
```{r prepare timecourse data}
rm(justone_test, lucy_plots, test)

# import the timecourse

tmp.df4_full_stim_downs_jun2021 <- readRDS("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/tmp.df4_full_stim_downs_jun2021.rds")

# merge with behavioral data
unique(db_full4new_stim_screen_pupil_nopract$ssid)
# colnames(db_full4new_stim_screen_pupil_nopract)
# colnames(tmp.df4_full_stim_downs_jun2021)
# db_full4new_stim
# colnames(db_full4new_stim_screen_pupil_nopract)
db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]

# match types of merging variables
tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
db_full4new_stim_subset$ssid<- as.character(db_full4new_stim_subset$ssid)

# tNo
tmp.df4_full_stim_downs_jun2021_with_beh2$tNo <- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
db_full4new_stim_subset$tNo <- as.character(db_full4new_stim_subset$tNo)
unique(db_full4new_stim_subset$tNo)
unique(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)

# merge
nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
# 87529

table(is.na(db_full4new_stim_subset$mediansplit_self_valence))

tmp.df4_full_stim_downs_jun2021_with_beh2$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
tmp.df4_full_stim_downs_jun2021_with_beh2<- tmp.df4_full_stim_downs_jun2021_with_beh2%>%
  arrange(ssid,tNo, timerezero3)

tmp.df4_full_stim_downs_jun2021_with_beh<- left_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset)

db_full4new_stim_subset$tNo<- as.numeric(db_full4new_stim_subset$tNo)

table(is.na(db_full4new_stim_subset$arousal))

tmp.df4_full_stim_downs_jun2021_with_behnew<- right_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset,
                                                     by = c('ssid', 'tNo'))

nrow(tmp.df4_full_stim_downs_jun2021_with_beh)
# 172168 good

nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
# 87529
nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)

table(is.na(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_self_valence))

Quick check that things make sense
```{r}
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

# group_by(stimIAPS)%>%
tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample >= 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

let's test the interaction term
```{r}
nrow(nbins)
nbins = 30 # number of bins

# create and empty dataframe for the timecourse analyses
timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

# View(timecourse_result_df)
nbins<- nbins[1:28]

i = 0 # remember to always rezero it
# b = 10

rm(i,b)

nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c* valence+Mean_gray_z  +
                                (1 | ssid)+
                                (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    # mediansplit_self_valence == "More positive" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_result_df_int[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_int[i,2]<- lmer_bin_pup_summary[["coefficients"]][5,1] # first number is term(row), second is column
            timecourse_result_df_int[i,3]<-lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_result_df_int[i,4]<-lmer_bin_pup_summary[["coefficients"]][5,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_int[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

# timecourse_result_df_pos<- timecourse_result_df

timecourse_result_df_int %>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)
